%-------------------------
% Resume in Latex
% Author : Sriharsha Mopidevi
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----Custom Update----------
\usepackage{ragged2e}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyhead{} % clear all header fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{3.60004pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      {\small#1} & {\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----GPA------
\newcommand{\resumeSubheadingWithGPA}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      {\small#3} $|$ {\small \textbf{GPA}: #4} & {} {\small #5}
    \end{tabular*}\vspace{-7pt}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    {\Huge \scshape Venkata Sai Sri Harsha Mopidevi} \\ 
    % \vspace{1pt} 198 Tonnele Ave, Jeresey City, NJ 07306\\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 571-295-2881 \hspace{3pt} 
    \href{mailto:sriharshamvs@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \textcolor{blue}{\underline{sriharshamvs@gmail.com}}} \hspace{3pt}
    \href{https://www.linkedin.com/in/sriharshamvs/}{\raisebox{-0.2\height}\faLinkedin\ \textcolor{blue}{\underline{linkedin.com/in/sriharshamvs}}} \hspace{3pt}
    \href{https://github.com/sriharshamvs}{\raisebox{-0.2\height}\faGithub\ \textcolor{blue}{\underline{github.com/sriharshamvs}}} \hspace{3pt}
    \vspace{2pt}\href{https://blog.sriharshamvs.com/}{\raisebox{-0.2\height}\faBlogger\ \textcolor{blue}{\underline{blog.sriharshamvs.com}}}


\end{center}


%-----------SUMMARY-----------
\section{SUMMARY}
\begin{justify}\small
Full Stack Software Engineer with 3+ years of experience specializing in Node.js and Java backend development, complemented with frontend proficiency in JavaScript, TypeScript, and ReactJS. Strong experience in Express.js and Spring Boot for building robust and scalable backend services. Additional experience with Python-based frameworks like Django and Flask, as well as NextJS. Proficient in managing cloud infrastructure using AWS, developing serverless applications, and implementing RESTful API architecture. Demonstrates a deep understanding of algorithms, data structures, and version control using Git.
\end{justify}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart
    \resumeSubheading
      {GSPAN}{August 2019 -- January 2022}
      {Software Engineer}{New Delhi, India}
      \resumeItemListStart
        \resumeItem{Developed a lightweight Progressive Web Application for User Management System using a variety of technologies, including Nextjs, Java, and Spring Boot. This system streamlined organizational administrative tasks, increasing overall productivity by 25\%.}
        \resumeItem{Designed and implemented a Serverless architecture using Netlify and AWS Lambda functions for various projects across the organization. This implementation reduced operational and deployment costs by 70\%.}
        \resumeItem{Increased website traffic 5x by developing an interactive web-app, using Deckgl, Mapbox, and React-vis, to visualize Indian election and COVID-19 data, in collaboration with designers and project managers.}
        \resumeItem{Built fully automated ETL scripts and pipelines using Python, facilitating the publishing of RESTful API endpoints. This automation made data more accessible for cross-organizational use, leading to a 60\% increase in team productivity.}
        \resumeItem{Created reusable React components using React-vis, Deckgl, and Recharts, resulted in 2x development speed for various projects and enhancing data comprehension for non-technical stakeholders.}
        \resumeItem{Provisioned a cloud-native Apache Superset application for quick data exploration and data visualization, boosting data-driven decisions by 35\% across the team.}
      \resumeItemListEnd

    \resumeSubheading
      {Swecha}{December 2018 -- July 2019}
      {Software Devloper Intern}{Hyderabd, India}
      \resumeItemListStart
        \resumeItem{Conceptualized and implemented sensor module libraries using C, leading to an impressive enhancement of code readability by 80\%.}
        \resumeItem{Assisted in a significant front-end re-factorization process utilizing Vue.js, which expedited loading speed by 43\%.}
        \resumeItem{Developed unit tests and boosted the code coverage by 82\% on all features using Cypress \& Selenium.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming/ Scripting Languages}: \hspace{18pt} Python, JavaScript, C, Java, TypeScript, Node.js, HTML/CSS, Shell, SQL  \\[2pt]
     \textbf{Software Development Methodologies}: \hspace{7pt} Agile, Scrum, Continuous Integration, Continuous Delivery \\[2pt]
     \textbf{Frameworks \& Libraries}: \hspace{66pt} Django, Next.js, React, React Native, Spring, Spring Boot, Express, Vue.js, Recoil, Pandas \\[2pt]
     \textbf{Database Management}: \hspace{71pt} PostgreSQL, MySQL, Oracle, NoSQL, MongoDB\\[2pt]
     \textbf{Tools \& Services}: \hspace{99pt} Linux, Git, Docker, AWS, Jenkins, Jira, Serverless, REST web services, Microservices\\[2pt]
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheadingWithGPA
      {PACE University, Seidenberg School of Computer Science and Information Systems}{January 2022 -- May 2023}
      {Master in Science (MS) Computer Science} {3.82/4.0} {New York, NY}
      \vspace{5pt}
    \resumeSubheadingWithGPA
      {ACE Engineering College}{May 2019}
      {Bachelor of Technology (B.Tech) Electronics and Communications} {3.4/4.0} {Hyderabad, India}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{PROJECTS}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Health App} $|$ {Lead Software Engineer (Capstone Project)}}{}
          \resumeItemListStart
            \resumeItem{Collaborated with a team of 4 developers to develop an Android app using React Native, Recoil, and React Native Paper, enabling nutrition tracking and connections with fitness trainers and dietitians.}
            \resumeItem{Engineered backend services using Gin framework and database on AWS, along with an automated CI/CD pipeline using Jenkins to reduce mobile app deployment time by 50\%, ensuring seamless deployment and continuous testing.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Low Latency Live Streaming} $|$ {Software Engineer}}{}
          \resumeItemListStart
            \resumeItem{Deployed a cost-effective Open-Source Low Latency Live Streaming technology utilized by 200+ institutions during the COVID pandemic, demonstrating an understanding of the importance of low latency and performance for user perceptions of application quality.}
            \resumeItem{Built a containerized web application with Django framework, Postgres database for user authentication and streaming data, and an admin dashboard for user role and stream assignment, leading to an 80\% reduction in deployment time.}
          \resumeItemListEnd 
          
        \resumeProjectHeading
          {\textbf{Telegram Users Scraper} $|$ {Software Engineer}}{}
          \resumeItemListStart
            \resumeItem{Developed an Open Source Python-based Telegram User Scraper, facilitating data mining from Telegram groups and enhancing data collection efficiency by 40\%.}
            \resumeItem{The project's practicality and impact were well-received on GitHub, resulting in substantial contributions, numerous stars, and forks, demonstrating its significance and popularity within the tech community.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

%-----------VOLUNTEERING---------------
% \section{VOLUNTEERING}
%     \resumeSubHeadingListStart
%         \resumeSubheading{Free Software Movement of India}{Hyderabad, India}{Executive Committee Member}{August 2019 -- July 2022}
%             \resumeItemListStart
%                 \resumeItem{Trained 600+ students by conducting Bootcamp and workshops on Linux Administration, Python, and IoT.}
%                 \resumeItem{Recognized by various Free and Open Source communities, including FSMI and Mozilla, for expertise in web development and web plugins.}
%             \resumeItemListEnd
        
%     \resumeSubHeadingListEnd

\end{document}
